\LARGE \bf Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-04-13 paper.tex
Fixed refrence url's

Since the goal of this project is to optimize the flight time of a multirotor and then build it using existing remote controlled aircraft components, a NACA 0012 airfoil was used in the analysis for calculating the coefficient of lift, $C_L$, and the blade element drag coefficient, $\delta$. This airfoil approximately represents the airfoil of many commonly used remote control helicopters \cite{mettler2013identification}. Data points for this airfoil were generated using Xfoil, an aerodynamics tool developed by The Massachusetts Institute of Technology. This data was then fit with polynomials to approximately represent $C_L$ and $\delta$ across a range of the angles of attack, $\alpha$, continuously, where $\alpha = \theta - \phi$.

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth]{pareto_front.png}
	\caption{Pareto fronter like curve found by optimizing for flight time given specified payloads.}
		\label{fig:payload}
\end{figure}

@@

Because the final design requires a single optimal solution and not a range of solutions that depend on our payload capacity we then simultaneously optimize at several payloads. This means the optimization must maximize the total combined flight time while stratifying constraints for operating points.

@@

When simultaneously optimizing with 3, 5, and 7 kg payloads we get an optimal solution. The solution flight time is at least 42.46 minutes with a payload less then 7 kg. The values of the optimal design variables can be seen in table~\ref{table:unbound_results}.

@@

The above solution is a vehicle with an unreasonably large slow moving propellers. While bounding our rotor size would give a more physically manageable solution, it would have also meant our optimization was largely an aerodynamic analysis with a small optimization of engine size. Leaving the variable loosely bounded gives more insight about the trade offs of the vehicle makes for efficiency.

We also found that the solutions varied greatly with very small changes in our aerodynamic analysis. Personal experience with RC aircraft lead us to believe that the head speed and pitch angles are too extreme. Further validation of our analysis would be required before a design such as this to be built.

>>>>

Since the goal of this project is to optimize the flight time of a multirotor and then build it using existing remote controlled aircraft components, a NACA 0012 airfoil (see \cite{abbott1959theory}) was used in the analysis for calculating the coefficient of lift, $C_L$, and the blade element drag coefficient, $\delta$. This airfoil approximately represents the airfoil of many commonly used remote control helicopters \cite{mettler2013identification}. Data points for this airfoil were generated using Xfoil, an aerodynamics tool developed by The Massachusetts Institute of Technology. This data was then fit with polynomials to approximately represent $C_L$ and $\delta$ across a range of the angles of attack, $\alpha$, continuously, where $\alpha = \theta - \phi$.

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth]{pareto_front.png}
	\caption{Pareto frontier-like curve found by optimizing for flight time given specified payloads.}
		\label{fig:payload}
\end{figure}

@@

Because the final design requires a single optimal solution and not a range of solutions that depend on our payload capacity, we then simultaneously optimized at several payloads. This means the optimization must maximize the total combined flight time while satisfying constraints for operating points.

@@

When simultaneously optimizing with 3, 5, and 7 kg payloads our optimizer converges to an optimal solution. The solution flight time is at least 42.46 minutes with a payload less then 7 kg. The values of the optimal design variables can be seen in table~\ref{table:unbound_results}.

@@

The above solution is a vehicle with unreasonably large, slow moving propellers. While bounding our rotor size would give a more physically manageable solution, it would have also meant our optimization was largely an aerodynamic analysis with a small optimization of engine size. Leaving the variable loosely bounded gives more insight about the trade-offs the vehicle makes for efficiency.

We also found that the solutions varied greatly with very small changes in our aerodynamic analysis. Personal experience with RC aircraft leads us to believe that the head speed and pitch angles are too extreme. Further validation of our analysis would be required before a design such as this were to be built.
